Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-01-13 papers/01 Reply round 1/response_TSG.tex

\query[R3-3]{As well pointed by the authors, this is a semi-decentralized approach where a coordinator is needed. Please, provide some discussion on how this is different with community-based local markets.   }
\ans{As discussed in \cite[Sect. 3.2]{sousa2019}, in community-based local markets, each prosumer  does not know with which other prosumers it trades energy. The power balance of the whole network (all prosumers) is considered. Our setup considers full P2P markets where each prosumer knows its trading partners and, thus, negotiates directly with them. The coordinator in our setup plays a role in handling the physical constraints of the network as well as the aggregated power bought from the main grid.}

\query[R3-4]{ The proposed algorithm relies on several dual variables. Please, elaborate on the meaning of this dual variables and their interpretation as economic outputs of the clearing process. }
%
\ans{\green{
We have included a paragraph in Section III B in which we list all primal, dual, and auxiliary variables of the main algorithm, along with an explanation of their scope, and economical and system-theoretic interpretations.
}}
%
%\ans{We introduce dual variables for the purpose of problem decomposition. Particularly, these dual variables are associated with the coupling constraints that define $\mc C$ in \red{(9)}. Some of these dual variables, i.e., particularly those that are associated with bus power balance constraints \red{(13)} and reciprocity constraints \red{(8b)}, can be intrepreted as  nodal prices and bilateral trading prices, respectively, as discussed in \cite[Section 2.4]{lecadre2020}. }

\query[R3-5]{As to the results section, I miss some analysis of trading prices. Please consider to add some information about transactions prices among peers and compare them with grid prices. This analysis might be interesting in both storage and non-storage situations.}
\ans{For the simulations in Section IV-C, we consider a uniform per-unit trading price $c_{(i,j)}^{\mathrm{tr}}=0.08$ and trading tariff $c^{\mathrm{ta}}=0.01$, for all trading links $(i,j) \in \mc E$. Figure 8 in the revised manuscript show how the average trading prices $c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$ compares with the electricity price from the main grid ($c^{\mathrm{mg}}$). The relatively low trading prices explain high power traded among the prosumers. We can also observe from the top plot that during the first six hours, these prices are almost equal, thus the amount of power traded is relatively low (see Figure 7 in the revised manuscript) . }

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{figures/simB_0402_pt3_v2.eps}
	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
	}
	\label{fig:simC_pen}
\end{figure}

### 2022-01-13 papers/02 journal v2/journal_v14.tex
fig 9

\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
\end{itemize}
From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage. From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
}

\begin{figure}
\marginnote{\note{R1-6}}
\edit{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 1}. Coordinated P2P Market Clearing
\smallskip
\hrule 
\smallskip
\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$. DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\! 0$, $\mu_y^{\text{pb}}(0)\! = \!0$, $\forall y \!\in\! \mc B$.

\medskip
 \text{Iterate until convergence $(k = 0,1,\ldots)$}
\begin{align*}
& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
\quad &\left|
\begin{array}{l}
\text{Local update via \textsc{Algorithm 2}:}\\
\left|
\begin{array}{l}
\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
\end{array}
\right.\\[1em]
 \text{Communication}\\
 \left|
\begin{array}{l}
\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
 \left|
\begin{array}{l}
p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
\end{array}
\right.
\end{array}
\right.
\end{array}
\right.\\[.5em]
%%%
% DNO
%%%
& \text{DNO}\\
\quad &\left|
\begin{array}{l}
\text{Central update via \textsc{Algorithm 3}:}\\
\left|
\begin{array}{l}
\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
\end{array}
\right.\\[1em]
\text{Communication (Gather \& Broadcast)}\\
 \left|
\begin{array}{l}
\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
 \left|
\begin{array}{l}
\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}} \text{ on bus } y%
\end{array}%
\right.%
\end{array}%
\right.\\[1em]
\end{array}%
\right.%
\end{align*}
\smallskip
\hrule
\end{minipage}
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=.5\textwidth]{figures/algorithm1_GB_v4}
%\caption{Information flow of Algorithm~1 for each prosumer $i \in \mc N$ (top boxes) and the DNO (bottom box).}
%\label{fig:IFC}
%\end{figure}

@@

\begin{figure}[t]
	\centering\marginnote{\note{R3-6}} 
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3}
	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
	\label{fig:sim_B1}
\end{figure}
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4}
	\caption{Aggregated P2P trading in scenarios (a) and (b).
	}
	\label{fig:sim_B2}
\end{figure}  
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\marginnote{\note{R3-5}}
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v1}
	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
	}
	\label{fig:sim_B3}
\end{figure}  
\iffalse 
\begin{figure}[!t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simC_37_v2.eps}
	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
	}
	\label{fig:simC}
\end{figure}
\fi 
%\clearpage

>>>>

\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
\end{itemize}
From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage. From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
}
%
\begin{figure}[t]
\centering
\includegraphics[width=.4\textwidth]{figures/flowChart_v1}
\caption{Flow chart of Algorithm 1.}
\label{fig:IFC}
\end{figure}
%
\begin{figure}[t]
\marginnote{\note{R1-6}}
\edit{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 1}. Coordinated P2P Market Clearing
\smallskip
\hrule 
\smallskip
\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$. DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\! 0$, $\mu_y^{\text{pb}}(0)\! = \!0$, $\forall y \!\in\! \mc B$.

\medskip
 \text{Iterate until convergence $(k = 0,1,\ldots)$}
\begin{align*}
& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
\quad &\left|
\begin{array}{l}
\text{Local update via \textsc{Algorithm 2}:}\\
\left|
\begin{array}{l}
\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
\end{array}
\right.\\[1em]
 \text{Communication}\\
 \left|
\begin{array}{l}
\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
 \left|
\begin{array}{l}
p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
\end{array}
\right.
\end{array}
\right.
\end{array}
\right.\\[.5em]
%%%
% DNO
%%%
& \text{DNO}\\
\quad &\left|
\begin{array}{l}
\text{Central update via \textsc{Algorithm 3}:}\\
\left|
\begin{array}{l}
\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
\end{array}
\right.\\[1em]
\text{Communication (Gather \& Broadcast)}\\
 \left|
\begin{array}{l}
\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
 \left|
\begin{array}{l}
\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}} \text{ on bus } y%
\end{array}%
\right.%
\end{array}%
\right.\\[1em]
\end{array}%
\right.%
\end{align*}
\smallskip
\hrule
\end{minipage}
}
\end{figure}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\begin{figure}[t]
	\centering\marginnote{\note{R3-6}} 
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt1_v3}
	\caption{	Incorporating storage units causes a peak-shaving effect on the sum of the total power imported from the main grid and the power locally generated.}
	\label{fig:sim_B1}
\end{figure}
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt2_v4}
	\caption{Aggregated P2P trading in scenarios (a) and (b).
	}
	\label{fig:sim_B2}
\end{figure}  
\begin{figure}[t]
	\centering 
	%\hspace{-17pt}
	\marginnote{\note{R3-5}}
	\includegraphics[width=1\linewidth]{figures/simB_0402_pt3_v2}
	\caption{Comparison of the average electricity trading price ($c^{\mathrm{tr}} + c^{\mathrm{ta}} + \tfrac{1}{|\mc E|}\sum_{(i,j)\in \mc E}\mu_{(i,j)}^{\mathrm{tr}}$) with the electricity grid prices ($c^{\mathrm{mg}}$) in scenarios a (top) and b (bottom).
	}
	\label{fig:sim_B3}
\end{figure}  
\iffalse 
\begin{figure}[!t]
	\centering
	\includegraphics[width=1\linewidth]{figures/simC_37_v2.eps}
	\caption{\textcolor{red}{[OLD]} Peak shaving effect with different per-unit cost of using storage.
	}
	\label{fig:simC}
\end{figure}
\fi 
%\clearpage
